Replication of \"Anti-Immigrant Rhetoric and ICE Reporting Interest: Evidence

### 2024-07-03 paper_replication_final.Rmd
fixing
final touch of the paper is done

```{r, warning=FALSE}
library(stm)
load("from_replication_files/TopicModel.Rdata")
document_topics <- make.dt(immigrFit, meta = out$meta)
topic_terms <- t(exp(immigrFit$beta$logbeta[[1]]))
rownames(topic_terms) <- out$vocab
colnames(topic_terms) <- sprintf("Topic%d", 1:ncol(topic_terms))
```

@@

ice <-
  read_csv("from_google_trends/ice_reportings.csv", skip = 4, col_names = c("year", "month", "reports", "reports_convicted", "", "", "", "reports_non_criminal", "", ""))|>
  select(c(1, 2, 3, 4, 8))|>
  fill(year, .direction = "down")|> 
  filter(month != "Total")|>
  mutate(
    month = match(month, month.name),
    date = make_date(year, month)
  )

>>>>

```{r, warning=FALSE}
library(stm)
load("from_replication_files/topic_model_lite.Rdata")
# document_topics <- make.dt(immigrFit, meta = out$meta)
# topic_terms <- t(exp(immigrFit$beta$logbeta[[1]]))
# rownames(topic_terms) <- out$vocab
# colnames(topic_terms) <- sprintf("Topic%d", 1:ncol(topic_terms))
```

@@

ice <-
  read_csv("extended_research/ice_reportings.csv", skip = 4, col_names = c("year", "month", "reports", "reports_convicted", "", "", "", "reports_non_criminal", "", ""))|>
  select(c(1, 2, 3, 4, 8))|>
  fill(year, .direction = "down")|> 
  filter(month != "Total")|>
  mutate(
    month = match(month, month.name),
    date = make_date(year, month)
  )
